---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# mlms

<!-- badges: start -->
<!-- badges: end -->

The mlms(mixed linear model selector) is an R package to build linear models with adjustment of covariants. Each potential covariate in the `Z` data frame is frist tested whether it iscorrelated with any variable in X. For any variable in `X`, only the covariants in `Z` that has a p-value < 0.1 is used to adjust the variance in the complete model. Next, the covariants are tested whether they are significantin the complete model. Finally, the complete model is fit to test the effect of the target coefficient.

## Installation

```{r, eval=FALSE}
devtools::install_github("zhuchcn/mlms")
```

## Data

An example dataset `growth` is included in the package. The dataset has 80 observations of infant growth at 18 month from a nutritional supplementation study.

```{r}
library(mlms)
data(growth)
```

## Example

Create the data frame `X` for outcome variables

```{r}
X = growth[,1:3]
head(X)
```

Create the design matrix

```{r}
design = model.matrix(~ treatment, data = growth)
head(design)
```

Create the data frame `Z` for potential covariants

```{r}
Z = growth[, 5:10]
```

Run model selection

```{r}
fit_mlms(X, design, Z, coef = "treatmentLNS")
```
